Fourmile Calibrations

### 2022-12-06 calibration_output.Rmd
working on hydrographs and kge

library(tidyverse)
library(plotly)

@@

## Hydrographs

```{r}

flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA)

@@

library(hydroGOF)

KGE(flow$grid_all, flow$obs)
KGE(flow$statn_all, flow$obs)

get_kge <- function() {

}

@@

>>>>

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)

@@

## Hydrograph

```{r hydrographs, echo = F}
flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA)

@@

library(hydroGOF)
```

## Overall KGE

```{r kge overall, echo = F}

flow_kge_all <- flow %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge_all <- flow_kge_all %>%
  pivot_longer(everything()) %>%
  arrange(value)

kable(flow_kge_all) %>%
  kable_styling()

@@

## Model run KGE by water year

```{r kge by year, echo = F}
flow_year <- flow %>%
  mutate(WY = addWaterYear()) %>%
  group_by(WY) %>%
  summarize(kge_grid2011 = KGE(grid_2011, obs),
            kge_grid2012 = KGE(grid_2012, obs),
            kge_grid2013 = KGE(grid_2013, obs),
            kge_grid2014 = KGE(grid_2014, obs),
            kge_grid2015 = KGE(grid_2015, obs),
            kge_grid2016 = KGE(grid_2016, obs),
            kge_grid2017 = KGE(grid_2017, obs),
            kge_grid2018 = KGE(grid_2018, obs),
            kge_grid2019 = KGE(grid_2019, obs),
            kge_grid2020 = KGE(grid_2020, obs),
            kge_gridall = KGE(grid_all, obs),
            kge_statn2011 = KGE(statn_2011, obs),
            kge_statn2012 = KGE(statn_2012, obs),
            kge_statn2013 = KGE(statn_2013, obs),
            kge_statn2014 = KGE(statn_2014, obs),
            kge_statn2015 = KGE(statn_2015, obs),
            kge_statn2016 = KGE(statn_2016, obs),
            kge_statn2017 = KGE(statn_2017, obs),
            kge_statn2018 = KGE(statn_2018, obs),
            kge_statn2019 = KGE(statn_2019, obs),
            kge_statn2020 = KGE(statn_2020, obs),
            kge_statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  pivot_wider(names_from = 'year', values_from = 'kge')

kable(flow_kge) %>%
  kable_styling()
